---
title: "yfinance showcase"
output: html_notebook
---

```{r}
# remotes::install_github("ljupch0/yfinance")

library(yfinance)
library(tidyverse)
```




Find the yahoo finance ticker need to pull data for your group of companies. 
```{r}

# ISIN Codes
search_stock(search_term = "US4581401001", keep_results = "top")


# CUSIP Codes
search_stock(search_term = "594918104", keep_results = "top")


# Company Names
companies <- c("Novo Nordisk", "Regeneron Pharmaceuticals Inc.", "Alexion Pharmaceuticals Inc.", "Vertex Pharmaceuticals Inc.", "Jazz Pharmaceuticals", "Incyte Corp.", "Biomarin Pharmaceutical Inc.", "United Therapeutics Corp.")

# Search and return all results
yfinance::search_stock(search_term = "Novo Nordisk", keep_results = "all")


# Search and return top results
yfinance::search_stock(search_term = companies, keep_results = "top")



```



WRONG TICKERS
```{r}
result <- get_cf(ticker = "APPL") # wrong ticker APPL instead of AAPL

attributes(result)
```




CURRENT and GENERAL DATA

# If you already have tickers, you can cleanly get company names
```{r}
yfinance::get_company_names(ticker = c("AAPL", "MSFT"))
```

# Get stock sector, industry, business description and other. Useful if making presentations.
```{r}
get_summaries(ticker = c("DUK", "DXC"))
```


# Last trading day price, volume, market cap
```{r}
yfinance::get_price(ticker = "AA")
```



HISTORICAL FINANCIAL Data


```{r}
# Cash Flow
get_cf(ticker = c("ADSK", "CMG"), report_type = "annual")

get_cf(ticker = c("DE", "CAT"), report_type = "quarterly")

# Balance Sheet
get_bs(ticker = c("KO", "COP"), report_type = "quarterly")

# Income Statement
get_income(ticker = c("C", "BAC"), report_type = "quarterly")
```



# Nested Data
```{r}
biotech_balance_sheets <- tibble(
  companies = companies
) %>% 
  mutate(
    ticker = yfinance::search_stock(search_term = companies, keep_results = "top")$symbol,
    full_name = yfinance::search_stock(search_term = companies, keep_results = "top")$longname,
  ) %>% 
  group_by(ticker) %>% # grouping is needed so that the data returned per company is only of that company. Otherwise every row will be the data of all companies together
  mutate(
    balance_sheet = list(yfinance::get_bs(ticker = ticker, report_type = "quarterly"))
  )

```

# Unnested Data
```{r}
biotech_financials <- yfinance::get_financials(ticker = biotech_balance_sheets$ticker, report_type = "quarterly") 

# Calculate Ratios
biotech_financials2 <- biotech_financials %>% 
  mutate(
    ebit_margin = ebit / totalRevenue
  )
  
# Plot Ratios  
biotech_financials2 %>% 
  group_by(ticker) %>% 
  dplyr::filter(date == last(date)) %>% 
  ungroup() %>% 
  ggplot()+
  geom_bar(mapping = aes(x = reorder(ticker, ebit_margin), y = ebit_margin, fill = ticker), stat="identity" )+
  theme_minimal()


```

